The aspects of integrated crop-livestock-forest system in Brazil

### 2022-07-07 iclfs_review/lit_review.Rmd
Wrote some aims of the review

>>>>

## Provide a rationale for the review

## Reference any previous reviews or meta-analyses on the topic

## State the aims and scope of the review (including its generality)

In this review I will analyse studies about ICLFS in Brazil. I pretend to answer several questions:

- Where are experiments on ICLFS being conducted?

- What are the characteristics of these systems? (species used, fertilizers, number of individuals per hectare, duration of the production cycle...)

- What are the fiber and food productivity in these systems?

- What is the amount of above ground carbon (alive and dead) being accumulated?

- What is the amount of below ground carbon being accumulated?

- What are the emissions of green house gases related to the ICLFS?

- What is the economic revenue from the adoption of the ICLFS?

## State the primary questions the review addresses (e.g. which moderators were tested)

## Describe whether effect sizes were derived from experimental and/or observational comparisons
